### 2021-06-18 sections/introduction.tex
a few more changes up to systematics

%The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
This paper is focused on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018. The corresponding integrated luminosity is 139.6 fb$^{-1}$. Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted and the signals are divided into several final states depending on the production modes and the
decay of $W$ boson hadronically and leptonically from the $t\rightarrow wb$ decay referred as $t_h$ and $t_l$. The $H\rightarrow \tau\tau$ decay detected to be in
either $\tlhad$ or $thadhad$ final states when the top decays hadronically ($t_h$) and only in $\thadhad$ when the top decay leptonically ($t_l$). 
Events with two hadronically decaying $\tau$-lepton candidate (\tauhad) without electron or muon are selected for hadronic channels. Events with at least one \tauhad with an additional electron or muon are selected from leptonic channels. More regions are exploited compared to the FCNC $\Htautau$ search conducted using partial Run~2 data.
The analysis also uses various $t\bar{t}$ control regions (CRtt) for calibration of tau fakes in Monte Carlo as well as
data-driven fake estimations from QCD multi-jet background.

>>>>

%The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
This paper is focused on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018. The corresponding integrated luminosity is 139.6 fb$^{-1}$. Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted and the signals are divided into several final states depending on the production modes and the
decay of $W$ boson hadronically and leptonically from the $t\rightarrow wb$ decay referred as $t_h$ and $t_l$. The $H\rightarrow \tau\tau$ decay detected to be in
either $\tlhad$ or $\thadhad$ final states when the top decays hadronically ($t_h$) and only in $\thadhad$ when the top decay leptonically ($t_l$). 
Events with two hadronically decaying $\tau$-lepton candidate (\tauhad) without electron or muon are selected for hadronic channels. Events with at least one \tauhad with an additional electron or muon are selected from leptonic channels. More regions are exploited compared to the FCNC $\Htautau$ search conducted using partial Run~2 data.
The analysis also uses various $t\bar{t}$ control regions (CRtt) for calibration of tau fakes in Monte Carlo as well as
data-driven fake estimations from QCD multi-jet background.

### 2021-06-18 sections/signal_background_modeling.tex
a few more changes up to systematics

In the leptonic channels, the events with real electron or muon and fake taus are modelled by calibrated monte carlo with scale factors
derived from the dedicated $t\bar t$
control regions ($CR_{tt}$) using the SM $t\bar t$ decay of dilepton events and semileptonically double-btagged lepton-jet events, summarized in Table~\ref{tab:crsr},
aimed at fake taus from different origins. There are four kinds of fake taus that need to be calibrated: Type1) $\tau_{W}$'s with the opposite charge to the lepton;
Type2) $\tau_{W}$'s with the same charge as the lepton; Type 3) the fake taus from b-jets; Type4) the fake taus from other origins (mainly radiations).
These control regions are similar to the signal regions but with an additional b-jet or lepton defined as:
$t_lt_l1b\thad$, $t_lt_l2b\thad$, $t_lt_h2b\thad$-2jSS, $t_lt_h2b\thad$-2jOS, $t_lt_h2b\thad$-3jSS, and $t_lt_h2b\thad$-3jOS.
Where di-lepton regions ($t_lt_l1b\thad$ and $t_lt_l2b\thad$) are used to calibrate the Type3 and Type4 fake taus. The regions of
$t_lt_h2b\thad$-2jOS and $t_lt_h2b\thad$-3jOS are used to calibrate Type1 fake taus. Similarly for the Type2, the regions of $t_lt_h2b\thad$-2jSS and $t_lt_h2b\thad$-3jSS are used.
A simultaneous fit to data is made to derive the scale factors for the fake taus, which consists of total 24 parameters including 3 $\pt$ bins (25-35, 35-45, 45-)GeV for 1 and 3
prong taus separately. The values of these scale factors range from 0.3 to 1.28 and are applied to the corresponding signal regions with single b-tagged jet.
In $t_l\thadhad$ channel, both taus can be fake, so the calibration is applied to each tau separately, following the same procedure as $\tlhad$ channels using the
lepton and fake tau charges, then the scale factors are multiplied together. The nominal value of the scale factors will vary along with other uncertainties from
combined preformace (CP) recommendations and theory uncertainties in the final fit.
%In the control regions with single lepton, $\met > 20$GeV and at least 2 light jets and 2 b-tagged jets are required to ensure that QCD contribution is negligible.
%The calibration is done depending on different source of the fake taus and \pt. The calibration factor are derived in the dedicated
%control regions discussed in Section~\ref{sec:strategy_Htautau}.

>>>>

In the leptonic channels, the events with real electron or muon and fake taus are modelled by calibrated monte carlo with scale factors
derived from the dedicated $t\bar t$
control regions ($CR_{tt}$) using the SM $t\bar t$ decay of dilepton events and semileptonically double-btagged lepton-jet events, summarized in Table~\ref{tab:srcr},
aimed at fake taus from different origins. There are four kinds of fake taus that need to be calibrated: Type1) $\tau_{W}$'s with the opposite charge to the lepton;
Type2) $\tau_{W}$'s with the same charge as the lepton; Type 3) the fake taus from b-jets; Type4) the fake taus from other origins (mainly radiations).
These control regions are similar to the signal regions but with an additional b-jet or lepton defined as:
$t_lt_l1b\thad$, $t_lt_l2b\thad$, $t_lt_h2b\thad$-2jSS, $t_lt_h2b\thad$-2jOS, $t_lt_h2b\thad$-3jSS, and $t_lt_h2b\thad$-3jOS.
Where di-lepton regions ($t_lt_l1b\thad$ and $t_lt_l2b\thad$) are used to calibrate the Type3 and Type4 fake taus. The regions of
$t_lt_h2b\thad$-2jOS and $t_lt_h2b\thad$-3jOS are used to calibrate Type1 fake taus. Similarly for the Type2, the regions of $t_lt_h2b\thad$-2jSS and $t_lt_h2b\thad$-3jSS are used.
A simultaneous fit to data is made to derive the scale factors for the fake taus, which consists of total 24 parameters including 3 $\pt$ bins (25-35, 35-45, 45-)GeV for 1 and 3
prong taus separately. The values of these scale factors range from 0.3 to 1.28 and are applied to the corresponding signal regions with single b-tagged jet.
In $t_l\thadhad$ channel, both taus can be fake, so the calibration is applied to each tau separately, following the same procedure as $\tlhad$ channels using the
lepton and fake tau charges, then the scale factors are multiplied together. The nominal value of the scale factors will vary along with other uncertainties from
combined preformace (CP) recommendations and theory uncertainties in the final fit.
%In the control regions with single lepton, $\met > 20$GeV and at least 2 light jets and 2 b-tagged jets are required to ensure that QCD contribution is negligible.
%The calibration is done depending on different source of the fake taus and \pt. The calibration factor are derived in the dedicated
%control regions discussed in Section~\ref{sec:strategy_Htautau}.

### 2021-06-18 sections/strategy_Htautau.tex
a few more changes up to systematics

This event categorisation is primarily motivated by the different quality of the event kinematic reconstruction, depending on the amount 
of $\met$ in the event (larger in $\lephad$ events compared with $\hadhad$ events), and whether a jet from the hadronic top-quark decay 
is missing or not (events with exactly three jets or at least four jets).
The event kinematic reconstruction is based on the strategy used in Ref.~\cite{Chen:2015nta}, and is summarised below.

For the decay mode events, the selected jets are assigned to the different top-quark decay products via a criterion based on 
minimising the angular distances between light flavor jets and the visible decay product of the Higgs boson (the two tau candidates).

@@

In the  $t_lt(qH)$ and $t_lH$ signal, the additional $q$ jet in the decay mode can still be found, but since the $W$ boson decays leptonically, there is a neutrino with large momentum and the flying direction is unknown. The kinematics fit is no longer feasible. The variables calculated from the visible objects are directly used in the multivariate analysis.

@@

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for hadronic channel. 
The description of each variable is provided in the text.}}
\input{\FCNCTables/Importance/xTFW/Merged}
\end{table*}

\begin{table*}[t!]
\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for leptonic channel. 
The description of each variable is provided in the text.}}
\input{\FCNCTables/Importance/tthML/Merged}
\end{table*}
%%%%%%%%%%%%%%%

Boosted decision trees are used in each SR to improve the separation between signal and background. 
%The separate training exploits differences in event kinematics across SRs.  
%draft 1 version
In the training, All signal events ($tuH$ and $tcH$ signal are merged with a ratio of 1:1) are used against the total SM background (including both real and fake $\had$ contributions).

@@

The BDT input variables in each SR and their importance are listed in Table~\ref{tab:mva_var} and defined in the following:

@@

\item $m_{\tau,\tau}$ is the invariant mass of the tau candidates and reconstructed neutrinos in $t_hH$ and $t_ht(qH)$ channels. 

@@

\item $m_{t,FCNC}$ is the visible invariant mass of the FCNC-decaying top quark reconstructed from di-tau candidates, FCNC-jet and reconstructed neutrinos.
\item $m_{\tau\tau,vis}$ is the visible invariant mass of the di-tau candidates

@@

\item $E_{\nu,i}/E_{\tau,i},i=1,2$ is the momentum fraction carried by the visible decay products from the tau mother. It is based on the best-fit 4-momentum of the neutrino(s) according to the event reconstruction algorithm in this section. For the $\tauhad$ decay mode, the visible decay products carry most of the tau energy since there is only a single neutrino in the final state, which is evident in the excess around 1 in Figure \ref{fig:x12_fit}. 

@@

\item $\Delta R(\tau,qjet)$ is the angular distance between the tau and the reconstructed fcnc jet.

@@

A comparison between data and the predicted background for some of these variables in each of the SRs considered is shown in Figures~\ref{fig:mva_input_hadhad} -~\ref{fig:mva_input_lhadhad}. The comparison between the data and predicted background after preselection for the distributions of two of the most 

@@

The expected signal (dashed red) corresponding to $\BR(t\to Hq)=0.2\%$ is also shown.

@@

The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{\FCNCFigures/tex/BDTinput}

\input{\FCNCFigures/tex/BDT}

>>>>

%This event categorisation is primarily motivated by the different quality of the event kinematic reconstruction, depending on the amount 
%of $\met$ in the event (larger in $\lephad$ events compared with $\hadhad$ events), and whether a jet from the hadronic top-quark decay 
%is missing or not (events with exactly three jets or at least four jets).
This event categorisation is primarily motivated by optimizing the sensitivity in each signal region that targets both leptonic and hadronic top-quark
decays as well as the Higgs decays into $\lephad$ or $\hadhad$ final state.   
The event kinematic reconstruction is further applied to suppress the background based on the strategy used in Ref.~\cite{Chen:2015nta}, and is summarised below.

For the $t_ht(qH)$ events, there should be at least four jets among which the one with the smallest angular distance to the visible decay product of the
Higgs boson (the two tau candidates) is considered as $q$-jet since the top decay products are likely boosted closer together than other jets. 
If there are more than 2 jets beside $q$-jet and $b$-jet, the jets from $W$ boson decay are chosen from the combination which have the invariant mass closest
to W resonance. There is the chance that one of the jets fails the $\pt$ requirement and not reconstructed. The FCNC top resonance is still reconstructable
given the big chance that the jet which is missing is from $W$ decay.

In the $t_hH$ events, there are 3 jets coming from top hadronic decay including the b-jet. So a Higgs resonance formed by the taus and a top resonance formed by
the jets are expected.

@@

In the  $t_lt(qH)$ and $t_lH$ signal, the additional $q$ jet in the decay mode can still be found, but since the $W$ boson decays leptonically, there is a neutrino with large momentum and the flying direction is unknown. The kinematics fit is no longer feasible in the $t_l\hadhad$ channel. The variables calculated from the visible objects are directly used in the multivariate analysis. However, the kinematics fit is still performed for the $t_l\had$ channels where the lepton and $\had$ are treated as di-tau candidate.

@@

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for hadronic channel. 
    The description of each variable is provided in the text.}}
\label{tab:importance_xTFW}
\input{\FCNCTables/Importance/xTFW/Merged}
\end{table*}

\begin{table*}[t!]
\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for leptonic channel. 
    The description of each variable is provided in the text.}}
\label{tab:importance_tthML}
\input{\FCNCTables/Importance/tthML/Merged}
\end{table*}
%%%%%%%%%%%%%%%

Boosted decision trees are used in each SR to improve the separation between signal and background. 
%The separate training exploits differences in event kinematics across SRs.  
%draft 1 version
In the training, All signal events ($tt(qH)$ and $tH$ signal are merged together) are used either for $tHu$ or $tHc$  $q=c,u$ against the total SM background (including both real and fake $\had$ contributions).

@@

The BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance_tthML}-~\ref{tab:importance_xTFW} and defined in the following:

@@

\item $m_{\tau,\tau}$ is the invariant mass of the tau candidates and reconstructed neutrinos in $t_hH$, $t_ht(qH)$, and $t_l\had$ channels. 

@@

\item $m_{t,FCNC}$ is the visible invariant mass of the FCNC-decaying top quark reconstructed from di-tau candidates, $q$-jet and reconstructed neutrinos.
\item $m_{\tau\tau,vis}$ is the visible invariant mass of the di-tau candidates or the lepton and $\had$ candidate when there is only one $\had$.

@@

\item $E_{\nu,i}/E_{\tau,i},i=1,2$ is the momentum fraction carried by the visible decay products from the tau mother. It is based on the best-fit 4-momentum of the neutrino(s) according to the event reconstruction algorithm in this section. For the $\tauhad$ decay mode, the visible decay products carry most of the tau energy since there is only a single neutrino in the final state.% which is evident in the excess around 1 in Figure \ref{fig:x12_fit}. 

@@

\item $\Delta R(\tau,qjet)$ is the angular distance between the tau and the reconstructed $q$-jet.

@@

A comparison between data and the predicted background for some of these variables in three main decay final states($t_l\hadhad$, $t_h\hadhad$, and $t_h\lephad$)
is shown in Figures~\ref{fig:mva_input_l2had_hadhad_lephad}.
%each of the SRs considered is shown in Figures~\ref{fig:mva_input_hadhad} -~\ref{fig:mva_input_lhadhad}.
The comparison between the data and predicted background after preselection for the distributions of two of the most 

@@

The expected signals (dashed red) are also shown after normalized to the total number of events un the predicted
background for the shape comparison of the distributions.   
%corresponding to $\BR(t\to Hq)=0.2\%$ is also shown.

@@

The final observable used to extract signal events is defined as the BDT distribution in each SRs corresponding to either $tHu$ or $tHc$ signal training.
Figure~\ref{fig:asimov_fitbdt_thu} and~\ref{fig:asimov_fitbdt_thc} show the fits to the data of BDT observable in each SRs with all background processes
constrained to the SM expectation.
%The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{\FCNCFigures/tex/BDTinput}

%\input{\FCNCFigures/tex/BDT}
